---
title: "Gun Control Chi"
author: "KL"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Kaitlyn and I am adding some text here to see if Ashley can get this file.

<<<<<<< HEAD
=======
Here is some more boring text for you to look at
>>>>>>> 081ba8da9bc5a03af6172cadd87d0e4b4759f438


#Creator
Getting gc_df.csv data, loading the tidyverse, and getting some summary counts
```{r}

library(tidyverse)
gc_df<- read_csv("gc_df.csv")

# filter function gets rid of NA's in the columns that we want
get_guns <- gc_df %>%
  filter(gender != "NA", make_get_guns != "NA")%>%
  count(gender, make_get_guns)%>%
  spread(make_get_guns, n)%>%
  select(-gender) #takes out the male and female column
  
rownames(get_guns) <- c("Female", "Male")
  
```

I am the collaborator and I am going to do Chi-Square. 

Question: is there a significant difference in gun control perspectives (as related to access to guns) for males and females?

Or, Is there a significant association between sex and gun control recommendations?

Or, Is perception of gun control access independent of sex?

Chi-Square
```{r}

#finding proportions ammong rows
guns_prop <- prop.table(as.matrix(get_guns), 1)

guns_prop

#do I actually think there is a sig difference in proportions across groups?
#perform chi square

guns_x2 <- chisq.test(get_guns)
guns_x2



```

Recommended government action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`)... , p < 0.001)


